---
title: "Presentation Ninja"
subtitle: "⚔<br/>with xaringan"
author: "Yihui Xie"
institute: "RStudio, PBC"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css:
      - default
      - ipa-fonts.css
      - custom.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "macros.js"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(ggeffects)
library(lme4)
library(brms)
options(htmltools.dir.version = FALSE)
xaringanExtra::use_xaringan_extra(c("panelset", "tachyons"))
```

```{r mald, echo=FALSE}
mald <- readRDS("./data/mald.rds")
```

# All about the Bayes

- Within the NHST (Frequentist) framework, the main analysis output is:

  - **Point estimates** of predictors' parameters (with standard error).
  - **P-values**.

- Within the Bayesian framework, the main analysis output is:

  - **Probability distributions** of predictors' parameters.

---

# All about the Bayes

Images of NHST vs Bayes output.

---

# An example

[Massive Auditory Lexical Decision](https://aphl.artsrn.ualberta.ca/?page_id=827) (Tucker et al. 2019):

- **MALD data set**: 521 subjects, RTs and accuracy.

- Subset of MALD: 30 subjects, 100 observations each.

--

```{r mald-print}
mald
```


---

# A frequentist linear model

```{r lm-1}
lm_1 <- lmer(
  log(RT) ~
    PhonLev +
    IsWord +
    PhonLev:IsWord +
    (1 | Subject),
  data = mald
)
```

---

# A frequentist linear model

```{r lm-1-sum}
summary(lm_1)
```

---

# A frequentist linear model

```{r lm-1-pred}
ggpredict(lm_1, terms = c("PhonLev", "IsWord")) %>%
  plot()
```

---

# Increase model complexity

**Try it yourself!** Does it work?

```{r lm-2, eval=FALSE}
lm_2 <- lmer(
  log(RT) ~
    PhonLev +
    IsWord +
    PhonLev:IsWord +
    (PhonLev + IsWord | Subject),
  data = mald
)
```

--

```{r lm-2-run, echo=FALSE}
lm_2 <- lmer(
  log(RT) ~
    PhonLev +
    IsWord +
    PhonLev:IsWord +
    (PhonLev + IsWord | Subject),
  data = mald
)
```

---

# A Bayesian linear model

```{r brm-1, eval=FALSE}
brm_1 <- brm(
  RT ~
    PhonLev +
    IsWord +
    PhonLev:IsWord +
    (PhonLev + IsWord | Subject),
  data = mald,
  # Let's use a lognormal fam, rather than log the RT values
  family = lognormal()
)
```

```{r brm-1-run, echo=FALSE}
brm_1 <- brm(
  RT ~
    PhonLev +
    IsWord +
    PhonLev:IsWord +
    (PhonLev + IsWord | Subject),
  data = mald,
  # Let's use a lognormal fam, rather than log the RT values
  family = lognormal(),
  # Technical stuff
  backend = "cmdstanr",
  cores = 4,
  threads = threading(2),
  file = "data/rds/brm_1"
)
```

---

# A Bayesian linear model

```{r brm-1-sum}
brm_1
```

---

# A Bayesian linear model

```{r brm-1-cond}
conditional_effects(brm_1, effects = "PhonLev:IsWord")
```

---

# Let's start small

**Try it yourself!**

```{r brm-2}
brm_2 <- brm(
  RT ~
    IsWord,
  data = mald,
  family = lognormal(),
  # Save model output to file
  file = "./data/rds/brm_2.rds"
)
```

---

class: center middle reverse

# [MCMC what?](https://chi-feng.github.io/mcmc-demo/app.html)

???

More on MCMC: http://elevanth.org/blog/2017/11/28/build-a-better-markov-chain/

---

# Let's start small

```{r brm-2-explain, eval=FALSE}
brm_2 <- brm(
  RT ~
    IsWord,
  data = mald,
  # Probability distribution of the OUTCOME
  family = lognormal(),
  # TECHNICAL STUFF
  # Save model output to file
  file = "./data/rds/brm_2.rds"
  # Number of chains
  chains = 4,
  # Number of iterations per chain
  iter = 2000,
  # Number of cores to use (each chain is run on each core)
  cores = 4
)
```

- `chains`: Number of MCMC chains to be run.

- `iter`: Number of iterations per MCMC chain.

- `cores`: Number of cores to use for running the MCMC chains.

  - You can find out how many cores your laptop has with `parallel::detectCores()`

---

# Let's start small

```{r brm-2-sum}
brm_2
```

